%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as thehttps://preview.overleaf.com/public/czwvvxzknjqj/images/fa6f8726841f80932e8ac6e4de79722de090a3cc.jpeg
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.7in,top=0.7in,right=0.7in,bottom=0.7in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{textcomp}
%\pagestyle{fancy}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Yukun (Vincent) Zeng} % Your name
\address{+1 (979)739 9315 \\ yzeng@tamu.edu}
\address{603 Ethel Blvd., Bryan, TX 77802} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
 % Your phone number and email
 
\fancyfoot{} % clear all footer fields
%\renewcommand{\headrulewidth}{0pt}
%\rhead{Seeking 2018 Full-time SDE/Big Data Positions}
\cfoot{\faGithub \hspace{0.10ex} \href{https://github.com/ykzeng/}{github.com/ykzeng/}
| \faLinkedin \hspace{0.10ex} \href{https://linkedin.com/in/yukunzeng/}{linkedin.com/in/yukunzeng/}}

\begin{document}
%\begin{rSection}{Objective}
%Seeking student assistant positions for 2017 fall, see \href{https://github.com/vincenttsang}{Github} and \href{https://parasol.tamu.edu/~yzeng/}{Homepage} for more info about me.
%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Texas A\&M University} \hfill {\bf College Station, TX} 
\\ Master of Science in Computer Science \hfill {\em Aug. 2016 - Aug. 2018}
\\ GPA: 3.57/4.00
\vspace*{-0.2em}

{\bf Harbin Institute of Technology} \hfill {\bf Weihai, China} 
\\ Bachelor of Engineering in Software Engineering \hfill {\em Sep. 2012 - July 2016}
\\ GPA: Overall 3.45/4.00, Major 3.70/4.00

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Campus Services}
%{\bf President} \hfill {HIT Robot Innovation Workshop} 
%\\{\bf Teaching Assistant} \hfill {School of Computer Sci. and Tech., HIT} 
%\\{\bf Research Assistant} \hfill {HIT-NS Joint R\&D Center} 
%\\{\bf Student Engineer} \hfill {HIT Network Center} 
% Technical Strenths
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Computer Languages &  C/C++, MATLAB \\
%Software \& Tools & HTML, LaTeX, Excel, Gerris, Mathematica, ASPEN Plus, Tecplot \\
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Work Experience}

{\bf Teaching Assistant} \hfill {Texas A\&M University} 
\\ {\em College Station, TX} \hfill {\em Jan. 2018 - Present}
\vspace*{-0.2em}

\begin{rSubsection}{Big Data Engineer Intern}{Big Data at AT\&T}{Dallas, TX}{June. - Aug. 2017}
\item Frauds detection by mining millions of billing records with \textbf{Hive} and \textbf{PySpark}, total profits \textasciitilde \$1.4M.
\item Index results using Apache \textbf{Solr} and visualize billing deviations with customizable plots (e.g., Heatmap) on \href{https://github.com/lucidworks/banana}{Banana}.
\item Deved National Access Mgmt. case tracker (full stack) with nice \textbf{Bootstrap} frontend that supports \textbf{AJAX} loading and autocompletion, \textbf{RESTful Java EE} backend and integrated it onto AAT Platform.
\item Workflow automation with \textbf{Jenkins}, programming and debugging experience on \textbf{Hadoop}, \textbf{Spark} and \textbf{Tez}.
\end{rSubsection}

\begin{rSubsection}{Grader}{College Station, TX}{Texas A\&M University}{Sep. 2016 - Dec. 2017}
\item Test case development and test automation for \href{http://faculty.cse.tamu.edu/dilma/web-csce410-fall16/index.htm}{CSCE 410 Operating Systems}, involving frame management, memory paging, virtual memory, thread scheduling, device driver and file systems.
\item Automated grading of \href{http://faculty.cse.tamu.edu/djimenez/312/}{CSCE 312 Computer Organization} coding assignments with \href{https://github.com/tamu-csce312/hw-test}{\textbf{bash} scripts}.
\end{rSubsection}

\begin{rSubsection}{Software Engineer Intern}{ARRIS Technology Co., Ltd.}{Shenzhen, China}{Jan. - May 2016}
\item Network programming with \textbf{C} in \textbf{embedded Linux}, \textbf{iptables} chain control, modem performance benchmarking.
\end{rSubsection}

\begin{rSubsection}{Technical Solution Intern}{Neusoft}{Dalian, China}{July 2014 - Aug. 2014}
\item Neusoft IM dev in Java with \textbf{socket}, \textbf{multithread} chating, chat history storage using \textbf{Oracle DB}.
\end{rSubsection}
\end{rSection}



\begin{rSection}{Selected Projects}
\begin{rSubsection}{\href{http://dota2rec.github.io}{D2Rec - Dota2 Hero Item Recommender System}}{Team Leader}{}{}
\item Crawled and preprocessed over 60,000 match records based on {\bf OpenDota}, analyzed and visualized hero-item correlations with {\bf Jupyter Notebook}.
\item Proposed {\bf baseline recommender} purely based on {\bf weighted item frequency} among matches, which performs pretty well in recommending general items that fit heroes' personality.
\item Proposed {\bf TDIPV} (Team Draft based Item Preference Variation) model to capture the {\bf use-against} and {\bf benefit-from} relations between enemies/allies and items.
\item Applied item classification and {\bf item combination process tracking} to focus on combined/final items while diminishing significance of intermediate/basic items thereby ensuring the {\bf quality of recommendation}.
\item Evaluated the system performance through both aspects of necissity and sufficiency, histograms and cumulative distributions show that with higher similarity an actual team's item is to our recommended item set, the chance of winning raises. An improvement from {\bf 0.68} to {\bf 0.83} is shown comparing TDIPV with baseline.
\item Preliminary work in correlating {\bf temporal effects} and {\bf team situation} with item purchase.
\end{rSubsection}

\begin{rSubsection}{\href{http://ieeexplore.ieee.org/document/7579961/}{Hi-Responsive Scheduling with MR Performance Prediction on Hadoop YARN}}{Research Assistant}{}{}
\item Pwd-less accessibility for scalable Hadoop cluster setup and job history tracking using \textbf{Hadoop REST APIs}.
\item Benchmark Hadoop cluster with FaceBook trace (\textasciitilde 6k Jobs) and heterogeneous MapReduce/Spark/Tez workloads. 
\item Size-based scheduler with \textbf{Linear Regression} job size prediction achieved \textbf{10x} faster response when heavily loaded.
\end{rSubsection}

\begin{rSubsection}{EmuEdge - Realistic Edge-Clouds Emulation with SDN on Xen}{Research Assistant}{}{}
\item Logged networking trace with \textbf{tc} and \textbf{iperf}, developed Android services for detailed sensor and wireless network data collection, such as accelerometer, lighting condition and wireless signal strength under a disaster scenario.
\item Leveraged \textbf{Open vSwitch} and Linux Kernel forwarding for comprehensive {\bf Software Defined Networking} within a single server, including network shaping, topology customization that supports hierarchical and realistic network for VMs running on Xen.
\end{rSubsection}

\begin{rSubsection}{Flash Vocabulary - Lightweight website for boosting vocabulary online}{Leader}{}{}
\item Deved a front-end library in \textbf{CSS} to create a universal UI, avoided unneccesary page reloading through \textbf{AJAX}.
\item Vocabulary pseudo-shuffling, reciting period arrangement based on \textbf{Ebinhaus} memory rules.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Jizhi Tutor Service - Online edu platform on Cloud}{Co-Leader}{}{}
\item Applied \textbf{HTML, CSS, Javascript (JQuery)} to the front-end dev, used complex \textbf{SQL Server} database (with \textbf{triggers}, \textbf{view}, \textbf{stored procedure}, etc) and \textbf{.NET} platform for data storage and business logic.
\item Lead the entire platform dev from designing, implementation to Cloud deployment and maintenance.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{General Coding - An APP to improve programmers' productivity}{Key Developer}{}{}
\item Used \textbf{fuzzy query} algorithm (Levenshtein Distance) to recommend similar APIs in our full-text API search engine.
\end{rSubsection}

\begin{rSubsection}{CSCE 614 Computer Architecture}{advised by Prof. Daniel A. Jimenez}{}{}
\item Cache behavior simulator with \textbf{LRU} and \textbf{random replacement} policies.
\item \href{https://github.com/vincenttsang/CompArch/blob/master/branch-predictor/p1-final-report/p1-final-report.pdf}{Fast path-based neural branch predictor with \textbf{perceptron}}.
\item \href{https://github.com/vincenttsang/CompArch/blob/master/cache-replacer/p2-final-report/p2-final-report.pdf}{High performance cache replacement using re-reference interval prediction (RRIP)}.
\end{rSubsection}


%------------------------------------------------

%\begin{rSubsection}{Motion Planning\&RoboDance Implementation}{May 2015 - Jan 2016}{Leader}{HIT Robot Innovation Workshop}
%\item Implemented a robot motion planning system and ensured the robot stability in the pose switch process.
%\item Programmed humanoid robot dance and solved the synchronization problem among multiple robots.
%\end{rSubsection}

%------------------------------------------------


\end{rSection}

%\begin{rSection}{Course Projects}
%{\bf CSCE 614 Computer Architecture}\hfill {\emph advised by Daniel A. Jimenez}\\
%Cache behavior simulator with LRU and random replacement policies.\\
%\href{https://github.com/vincenttsang/CompArch/blob/master/branch-predictor/p1-final-report/p1-final-report.pdf}{Fast path-based neural branch predictor with perceptron}.\\
%\href{https://github.com/vincenttsang/CompArch/blob/master/cache-replacer/p2-final-report/p2-final-report.pdf}{High performance cache replacement using re-reference interval prediction (RRIP)}.
%\end{rSection}

\begin{rSection}{Academic Experience}

\begin{rSubsection}{Graduate Researcher}{College Station, TX}{Parasol Lab, supervised by Prof. Nancy M. Amato}{Sep. 2016 - May 2017}
\item Worked with fundamental \textbf{C++} robotics libraries, like \href{https://parasol.tamu.edu/groups/amatogroup/research/UserGuided/Old/vizmo++/}{VIZMO++} and parallel computing library \href{https://parasol.tamu.edu/groups/rwergergroup/research/stapl/}{STAPL}.
\item Generalizing embedding graph, flow graph and dynamic region utilities used in \href{http://wafr2016.berkeley.edu/papers/WAFR_2016_paper_36.pdf}{Dynamic Region-biased RRT}.
\end{rSubsection}

\begin{rSubsection}{Team Leader}{Weihai, China}{HIT Robot Innovation Lab}{May 2015 - Jan. 2016}
\item Introduced matrix-based data structure for storing robot engine parameters and developed a stable gait planning system to produce RoboBasic codes for controlling engine motions.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Publications}
%{[1]Mengyuan Chao, }\underline{\bf Yukun Zeng}{ and Radu Stoleru. ``FCS: Feedback-based Customizable Scheduling For Stream Processing On Heterogeneous Mobile Devices.'' The 37th IEEE International Conference on Distributed Computing Systems (ICDCS 2017). \emph{In Progress}.
%}
%\vspace*{-0.2em}

{[1]Yang Liu, }\underline{\bf Yukun Zeng}{ and Xuefeng Piao. ``\href{http://ieeexplore.ieee.org/document/7579961/}{High-Responsive Scheduling with MapReduce Performance Prediction on Hadoop YARN.}'' Embedded and Real-Time Computing Systems and Applications (RTCSA), 2016 IEEE 22nd International Conference on. IEEE, 2016.
}

\end{rSection}

\begin{rSection}{Honors\&Awards}
{\bf Best Paper Award}{ for Outstanding Bachelor Dissertation} \hfill {July 2016}
\vspace*{-0.4em}

{\bf Meritorious Winner(1st Place)}{ in National Robot Championship} \hfill {July 2015}
\vspace*{-0.4em}

{\bf Honorable Mention}{ in Mathematical Contest in Modeling (MCM)} \hfill {Apr. 2015}
\vspace*{-0.4em}

{\bf 2nd Place}{ in HIT Software Design Competition} \hfill {Mar. 2014} 
\vspace*{-0.4em}

{\bf People's Scholarship} 5 times \hfill {Oct. 2013, Oct. 2014, May 2015, Oct. 2015, Apr. 2016}
\vspace*{-0.4em}

\end{rSection}

\begin{rSection}{Professional Activities}
{\bf Student Volunteer}\hfill Weihai, China\\
HIT-MSRA Human Language Technology Summer School\hfill {\emph July, 2013}
\vspace*{-0.2em}

{\bf Peer Reviewer}\hfill College Station, TX\\
IEEE Transactions on Robotics (T-RO)\\
IEEE Robotics and Automation Letters (RA-L)\\
Springer Journal of Intelligent \& Robotic Systems (JINT)\\
ACM Transactions on Spatial Algorithms and Systems (TSAS)\\
IEEE International Conference on Robotics and Automation (ICRA)\hfill {\emph Sep., 2016 - May, 2017}
\end{rSection}

\end{document}
